### 2024-06-25 basic-statistics.qmd
20240625 - power of mediation

- <https://www.causalevaluation.org/power-analysis.html> (web application: <https://powerupr.shinyapps.io/index/>)
- <https://webpower.psychstat.org/wiki/models/index>

>>>>

- <https://schoemanna.shinyapps.io/mc_power_med/>
- <https://www.causalevaluation.org/power-analysis.html> (web application: <https://powerupr.shinyapps.io/index/>)
- <https://webpower.psychstat.org/wiki/models/index>
